---
title: "Unit2_Climate Change"
output: html_document
---

Problem 1-1 - Creating Our First Model
```{r}
climate = read.csv("climate_change.csv")
climate_train = subset(climate, Year <= 2006)
climate_test = subset(climate, Year > 2006)

reg = lm(Temp ~ MEI + CO2 + CH4 + N2O + CFC.11 + CFC.12 + TSI + Aerosols, data = climate_train)
summary(reg)
```

Problem 2.2 - Understanding the Model
```{r}
cor(climate_train)
```

Problem 3 - Simplifying the Model
```{r}
reg2 = lm(Temp ~ MEI + TSI + Aerosols + N2O, data = climate_train)
summary(reg2)
```

Problem 4 - Automatically Building the Model
```{r}
stepreg = step(reg)
summary(stepreg)
```
It is interesting to note that the step function does not address the collinearity of the variables, except that adding highly correlated variables will not improve the R2 significantly. The consequence of this is that the step function will not necessarily produce a very interpretable model - just a model that has balanced quality and simplicity for a particular weighting of quality and simplicity (AIC).


Problem 5 - Testing on Unseen Data
```{r}
prediction = predict(stepreg, newdata = climate_test)
SSE = sum((prediction - climate_test$Temp)^2)
SST = sum((mean(climate_train$Temp) - climate_test$Temp)^2)
R2 = 1 - SSE / SST
R2
```











