---
title: "Unit2_ReadingTestScore"
output: pdf_document
---

Problem 1.1 - Dataset size
```{r}
pisaTrain = read.csv("pisa2009train.csv")
pisaTest = read.csv("pisa2009test.csv")
nrow(pisaTrain)
```

Problem 1.2 - Summarizing the dataset
```{r}
tapply(pisaTrain$readingScore, pisaTrain$male, mean)
```

Problem 1.3 - Locating missing values
```{r}
summary(pisaTrain)
```

Problem 1.4 - Removing missing values
```{r}
pisaTrain = na.omit(pisaTrain)
pisaTest = na.omit(pisaTest)

nrow(pisaTrain)
nrow(pisaTest)

```

Problem 2.2 - Unordered factors in regression models
To include unordered factors in a linear regression model, we define one level as the "reference level" and add a binary variable for each of the remaining levels. In this way, a factor with n levels is replaced by n-1 binary variables. The reference level is typically selected to be the most frequently occurring level in the dataset.


Problem 3.1 - Building a model
By default R selects the first level alphabetically ("American Indian/Alaska Native") as the reference level of our factor instead of the most common level ("White").
```{r}
pisaTrain$raceeth = relevel(pisaTrain$raceeth, "White")
pisaTest$raceeth = relevel(pisaTest$raceeth, "White")

# It would be time-consuming to type all the variables, but R provides the shorthand notation "readingScore ~ ." to mean "predict readingScore using all the other variables in the data frame." The period is used to replace listing out all of the independent variables.

lmScore = lm(readingScore ~ ., data=pisaTrain)
summary(lmScore)
```

Problem 3.2 - Computing the root-mean squared error of the model
```{r}
SSE = sum(lmScore$residuals^2)
RMSE = sqrt(SSE / nrow(pisaTrain))
RMSE
```

Problem 4.1 - Predicting on unseen data
```{r}
predTest = predict(lmScore, newdata = pisaTest)
summary(predTest)
max(predTest) - min(predTest)
```

Problem 4.2 - Test set SSE and RMSE
```{r}
SSE = sum((predTest - pisaTest$readingScore)^2)
RMSE = sqrt(SSE/nrow(pisaTest))
```

Problem 4.3 - Baseline prediction and test-set SSE
```{r}
mean(pisaTrain$readingScore)
SST = sum((mean(pisaTrain$readingScore) - pisaTest$readingScore)^2)
R2 = 1 - SSE / SST
R2
```










