---
title: "Uni3_Predicting Parole Violators"
output: pdf_document
---

Problem 1.1 - Loading the Dataset
Problem 1.2 - Loading the Dataset
```{r}
parole = read.csv("parole.csv")
nrow(parole) # 675
table(parole$violator)
```


Problem 2.1 - Preparing the Dataset
```{r}
str(parole)
summary(parole)
```

Problem 2.2 - Preparing the Dataset
```{r}
parole$state = as.factor(parole$state)
parole$crime = as.factor(parole$crime)
summary(parole)
```

Problem 3.1 - Splitting into a Training and Testing Set
```{r}
set.seed(144)
library(caTools)
split = sample.split(parole$violator, SplitRatio = 0.7)
train = subset(parole, split == T)
test = subset(parole, split == F)
table(train$violator)
```

Problem 4.1 - Building a Logistic Regression Model
```{r}
model = glm(violator ~ ., data = train, family = binomial)
summary(model)
```

Problem 5.1 - Evaluating the Model on the Testing Set
```{r}
predTest= predict(model, type = "response", newdata = test)
max(predTest)
```

Problem 5.2 - Evaluating the Model on the Testing Set
```{r}
table(test$violator, predTest > 0.5)

# Sensitivity = 12 / (12+11) = 0.522
# Specificity = 167  (167+12) = 0.933
# Accuracy = (167+12) / (167+12+12+11) = 0.886
```

Problem 5.3 - Evaluating the Model on the Testing Set
```{r}
table(parole$violator)

# Accuracy = 597 / (597+78) = 0.884
```

Problem 5.6 - Evaluating the Model on the Testing Set
```{r}
library(ROCR)
ROCRpred = prediction(predTest, test$violator)
as.numeric(performance(ROCRpred, "auc")@y.values)
```

Note that the dataset contains all individuals released from parole in 2004, either due to completing their parole term or violating the terms of their parole. However, it does not contain parolees who neither violated their parole nor completed their term in 2004, causing non-violators to be underrepresented. This is called "selection bias" or "selecting on the dependent variable," because only a subset of all relevant parolees were included in our analysis, based on our dependent variable in this analysis (parole violation). How could we improve our dataset to best address selection bias?























































































