---
title: "Unit3_Popularity of Songs Records"
output: pdf_document
---

Problem 1.1 - Understanding the Data
```{r}
song = read.csv("songs.csv")
nrow(subset(song, year == 2010))
```
Problem 1.2 - Understanding the Data
```{r}
nrow(subset(song, artistname == 'Michael Jackson'))

```

Problem 1.3 - Understanding the Data
```{r}
subset(song, artistname == 'Michael Jackson' & Top10 == 1)
```

Problem 1.4 - Understanding the Data
```{r}
table(song$timesignature)
```

Problem 1.5 - Understanding the Data
```{r}
song[which.max(song$tempo),]
```

Problem 2.1 - Creating Our Prediction Model
```{r}
SongsTrain = subset(song, year <= 2009)
SongsTest = subset(song, year > 2009)
nrow(SongsTrain)
```

Problem 2.2 - Creating our Prediction Model
```{r}
nonvars = c("year", "songtitle", "artistname", "songID", "artistID")
SongsTrain = SongsTrain[ , !(names(SongsTrain) %in% nonvars)]
SongsTest = SongsTest[ , !(names(SongsTest) %in% nonvars)]

mod1 = glm(Top10 ~ ., data = SongsTrain, family = binomial)
summary(mod1)
```

Problem 3.1 - Beware of Multicollinearity Issues!
```{r}
cor(song[c("loudness","energy")])
```

Problem 3.2 - Beware of Multicollinearity Issues!
Problem 3.3 - Beware of Multicollinearity Issues!
```{r}
SongsLog2 = glm(Top10 ~ . - loudness, data=SongsTrain, family=binomial)
# We just subtracted the variable loudness. 
# We couldn't do this with the variables "songtitle" and "artistname", 
# because they are not numeric variables, and we might get different values in the test set that the training set has never seen.
summary(SongsLog2)

SongsLog3 = glm(Top10 ~ . - energy, data=SongsTrain, family=binomial)
summary(SongsLog3)
```

Problem 4.1 - Validating Our Model
```{r}
predTest= predict(SongsLog3, type="response", newdata = SongsTest)
table(SongsTest$Top10, predTest > 0.45)
# (309+19)/(309+19+40+5) = 0.8793566
```

Problem 4.2 - Validating Our Model
```{r}
table(song$Top10)
# The baseline model would be to predict all 0.

table(SongsTest$Top10)
# 314 / (314+59)  = 0.8418231
```

Problem 4.3 - Validating Our Model
```{r}
table(SongsTest$Top10, predTest > 0.45)
```







































































